---
title: "Meta-Analysis Report: {{project_name}}"
author: "Meta-Analysis MCP Server"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 10
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
.libPaths(c("~/R/library", .libPaths()))
library(meta)
library(metafor)
library(ggplot2)
library(knitr)
library(DT)
```

# Executive Summary

This report presents the results of a systematic meta-analysis for **{{project_name}}**. The analysis included {{n_studies}} studies and employed {{analysis_method}} effects modeling.

## Key Findings

- **Pooled Effect Size**: {{pooled_effect}} (95% CI: {{confidence_interval}})
- **Heterogeneity (I²)**: {{heterogeneity_i2}}
- **Statistical Significance**: p = {{p_value}}

---

# Study Characteristics

```{r study_data, echo=FALSE}
# Load study data
data <- read.csv("../sample_data.csv")

# Display study characteristics table
datatable(data, 
          caption = "Table 1: Characteristics of included studies",
          options = list(pageLength = 10, scrollX = TRUE),
          class = 'cell-border stripe')
```

**Summary Statistics:**
- Total number of studies: `r nrow(data)`
- Total participants (treatment): `r if('n_treatment' %in% colnames(data)) sum(data$n_treatment, na.rm=TRUE) else 'N/A'`
- Total participants (control): `r if('n_control' %in% colnames(data)) sum(data$n_control, na.rm=TRUE) else 'N/A'`

---

# Meta-Analysis Results

```{r meta_analysis, echo=FALSE}
# Load meta-analysis results
results_file <- "../output_files/meta_analysis_results.json"
if (file.exists(results_file)) {
  results <- jsonlite::fromJSON(results_file)
  
  cat("## Overall Effect\n")
  cat("- **Pooled Effect Size (OR):** ", round(results$pooled_effect, 3), "\n")
  cat("- **95% Confidence Interval:** ", results$confidence_interval, "\n")
  cat("- **P-value:** ", format.pval(results$p_value, digits = 3), "\n")
  cat("- **Number of Studies:** ", results$n_studies, "\n\n")
  
  cat("## Heterogeneity Assessment\n")
  cat("- **I² Statistic:** ", results$heterogeneity_i2, "\n")
  cat("- **Tau² (between-study variance):** ", round(results$heterogeneity_tau2, 4), "\n")
  cat("- **Q Statistic:** ", round(results$heterogeneity_q, 2), "\n")
  cat("- **Heterogeneity P-value:** ", format.pval(results$heterogeneity_p, digits = 3), "\n")
}
```

### Interpretation

```{r interpretation, echo=FALSE, results='asis'}
if (exists("results")) {
  effect_size <- results$pooled_effect
  ci_lower <- as.numeric(gsub("\\[|\\]", "", strsplit(results$confidence_interval, ", ")[[1]][1]))
  ci_upper <- as.numeric(gsub("\\[|\\]", "", strsplit(results$confidence_interval, ", ")[[1]][2]))
  p_val <- results$p_value
  i2_numeric <- as.numeric(gsub("%", "", results$heterogeneity_i2))
  
  # Effect size interpretation
  if (effect_size > 1 && ci_lower > 1) {
    cat("The pooled analysis shows a **statistically significant increase** in the odds of the outcome.\n\n")
  } else if (effect_size < 1 && ci_upper < 1) {
    cat("The pooled analysis shows a **statistically significant decrease** in the odds of the outcome.\n\n")
  } else {
    cat("The pooled analysis shows **no statistically significant effect** on the outcome.\n\n")
  }
  
  # Heterogeneity interpretation
  if (i2_numeric < 25) {
    cat("**Low heterogeneity** (I² < 25%) suggests that the studies are relatively consistent.\n\n")
  } else if (i2_numeric < 50) {
    cat("**Moderate heterogeneity** (I² = 25-50%) suggests some variation between studies.\n\n")
  } else if (i2_numeric < 75) {
    cat("**Substantial heterogeneity** (I² = 50-75%) suggests considerable variation between studies.\n\n")
  } else {
    cat("**Considerable heterogeneity** (I² > 75%) suggests very high variation between studies.\n\n")
  }
}
```

---

# Forest Plot

```{r forest_plot, echo=FALSE, fig.cap="Figure 1: Forest plot showing individual study effects and pooled estimate"}
forest_plot_file <- "../output_files/forest_plot.png"
if (file.exists(forest_plot_file)) {
  knitr::include_graphics(forest_plot_file)
} else {
  cat("Forest plot not available.")
}
```

The forest plot displays the effect size and confidence interval for each individual study, along with the pooled estimate (diamond). The size of each square is proportional to the study's weight in the meta-analysis.

---

# Publication Bias Assessment

```{r publication_bias, echo=FALSE}
# Load publication bias results
bias_file <- "../output_files/publication_bias_results.json"
if (file.exists(bias_file)) {
  bias_results <- jsonlite::fromJSON(bias_file)
  
  cat("## Statistical Tests for Publication Bias\n\n")
  
  if (!is.null(bias_results$egger_test)) {
    cat("### Egger's Linear Regression Test\n")
    stat_val <- if(is.numeric(bias_results$egger_test$statistic)) round(bias_results$egger_test$statistic, 3) else bias_results$egger_test$statistic
    p_val <- if(is.numeric(bias_results$egger_test$p_value)) format.pval(bias_results$egger_test$p_value, digits = 3) else bias_results$egger_test$p_value
    cat("- **Test Statistic:** ", stat_val, "\n")
    cat("- **P-value:** ", p_val, "\n")
    if (is.numeric(bias_results$egger_test$p_value) && bias_results$egger_test$p_value < 0.05) {
      cat("- **Interpretation:** Significant evidence of publication bias (p < 0.05)\n\n")
    } else if (is.numeric(bias_results$egger_test$p_value)) {
      cat("- **Interpretation:** No significant evidence of publication bias (p ≥ 0.05)\n\n")
    } else {
      cat("- **Interpretation:** Statistical test results not available\n\n")
    }
  }
  
  if (!is.null(bias_results$begg_test)) {
    cat("### Begg's Rank Correlation Test\n")
    stat_val <- if(is.numeric(bias_results$begg_test$statistic)) round(bias_results$begg_test$statistic, 3) else bias_results$begg_test$statistic
    p_val <- if(is.numeric(bias_results$begg_test$p_value)) format.pval(bias_results$begg_test$p_value, digits = 3) else bias_results$begg_test$p_value
    cat("- **Test Statistic:** ", stat_val, "\n")
    cat("- **P-value:** ", p_val, "\n")
    if (is.numeric(bias_results$begg_test$p_value) && bias_results$begg_test$p_value < 0.05) {
      cat("- **Interpretation:** Significant evidence of publication bias (p < 0.05)\n\n")
    } else if (is.numeric(bias_results$begg_test$p_value)) {
      cat("- **Interpretation:** No significant evidence of publication bias (p ≥ 0.05)\n\n")
    } else {
      cat("- **Interpretation:** Statistical test results not available\n\n")
    }
  }
}
```

## Funnel Plot

```{r funnel_plot, echo=FALSE, fig.cap="Figure 2: Funnel plot for assessment of publication bias"}
funnel_plot_file <- "../output_files/funnel_plot.png"
if (file.exists(funnel_plot_file)) {
  knitr::include_graphics(funnel_plot_file)
} else {
  cat("Funnel plot not available.")
}
```

The funnel plot displays the relationship between study precision (standard error) and effect size. In the absence of publication bias, studies should be distributed symmetrically around the pooled estimate.

---

# Methods

## Search Strategy and Study Selection

This meta-analysis was conducted following PRISMA guidelines. Studies were included based on predefined inclusion and exclusion criteria.

## Statistical Analysis

- **Meta-analysis method:** {{analysis_method}} effects model
- **Effect measure:** {{effect_measure}}
- **Software:** R statistical software with the `meta` package
- **Heterogeneity assessment:** I² statistic and Cochran's Q test
- **Publication bias assessment:** Egger's test and Begg's test

## Quality Assessment

Study quality was assessed using appropriate tools for the study design. Details of the quality assessment are available in the supplementary materials.

---

# Limitations

1. **Heterogeneity:** {{heterogeneity_interpretation}}
2. **Publication bias:** Results should be interpreted considering potential publication bias
3. **Study quality:** The quality of individual studies may affect the overall conclusions
4. **Generalizability:** Results may not be generalizable to all populations or settings

---

# Conclusions

{{conclusions}}

---

# References

1. Borenstein, M., Hedges, L. V., Higgins, J. P., & Rothstein, H. R. (2021). Introduction to meta-analysis. John Wiley & Sons.
2. Higgins, J. P., & Thompson, S. G. (2002). Quantifying heterogeneity in a meta‐analysis. Statistics in medicine, 21(11), 1539-1558.
3. Egger, M., Smith, G. D., Schneider, M., & Minder, C. (1997). Bias in meta-analysis detected by a simple, graphical test. BMJ, 315(7109), 629-634.

---

*Report generated on `r Sys.Date()` using the Meta-Analysis MCP Server*
